Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-02 papers/FX/draft.tex
It is only the proof of convergence of mu((-inf, x]) = P(X <= x | X <= 0) -> Dirac[0] that is left to be proven.
K is a bigger problem!

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& \ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right) = \ln\left(
e^r + {\delta v - e^r \over \phi}
\right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < q(r, \phi)
\]
Naturally, if an agent invests in a risky asset instead of a riskless
bond, he expects to obtain a higher return from the risky asset than
he is guarranteed from the riskless bond. In our notation,
this means $\delta v > e^r$, which implies $q(r, \phi) > 0$.
The right-hand-side of \eqref{eq:functional} is a functional of the
distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\]
Hereafter we abbreviate $q(r, \phi)$ to just $q$. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=& \underbrace{
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \over (K - x)^{\alpha + 1}} dx
  }_{J_1} \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' - q)^\beta
    }
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}

\begin{theorem}
  Let
  \[
  G(\alpha, \beta, K, K') =
  \max_{0 < \phi \leq 1} \mathcal U F(\alpha, \beta, K, K', \phi)
  \]
  Let the disappointment threshold $C < \delta v$ be equivalent to $X < -q$. Assume
  \begin{equation}
    \label{eq:xxie1.1}
    K < {
      \alpha e^{1/\alpha} (1 - e^{-r})^\xi
      \over
      (\alpha + 1) A
    }
  \end{equation}
  where
  \[
  A = \max_{x \geq 1} {b x + x^{\alpha + 1} \over b + x^{\alpha + 1}}
  \]
  Then $G(\alpha, \beta, K, K')$ is monotonically increasing with $\alpha$.
\end{theorem}

\begin{proof}
  We show
  \[
  \td{G}{\alpha} > 0
  \]
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1}
    \mathcal U F(\alpha, \beta, K, K', \phi)
  \end{equation}
  We have
  \[
  G(\alpha, \beta, K, K') = \mathcal U F(\alpha, \beta, K, K', \hat \phi)
  \]
  It follows
  \begin{eqnarray}
    \td{G}{\alpha}
    &=&
    \pd{\mathcal U F}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    + \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi)
    \pd{\hat \phi}{\alpha}(\alpha, \beta, K, K')
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    &>& 0
  \end{eqnarray*}
  We have
    \begin{eqnarray*}
      && \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) \\
      &=&
      - \frac{\partial}{\partial \alpha} \left\{
        {\alpha p K^\alpha \over \xi} (1 + b)
        \int_{-\infty}^{0}
          \left[
            (1 - \hat\phi) e^r + \hat\phi e^x
          \right]^{-\xi}
          (K - x)^{-\alpha - 1}
        dx \right\} \\
      &=& \underbrace{
        {p \over \xi}
          (1 + b)\int_{0}^{\infty}
        \left[
          (1 - \hat\phi) e^r + \hat\phi e^{-x}
        \right]^{-\xi}
        \ln \left(
          1 + {x \over K}
        \right)
        {\alpha K^{\alpha} dx
          \over
          (K + x)^{\alpha + 1}
        }
      }_{L_1} \\
      && - \underbrace{
        {p \over \xi}
        (1 + b)\int_{0}^{\infty}
        \left[
          (1 - \hat\phi) e^r + \hat\phi e^{-x}
        \right]^{-\xi}
        {K^{\alpha} dx \over (K + x)^{\alpha + 1} }
      }_{L_2}
    \end{eqnarray*}
    Clearly $L_2 < \infty$. For $L_1$, observe
    \begin{eqnarray*}
      L_1 &<&
      {
        \alpha K^\alpha p (1 + b)
        \over
        \xi (1 - \hat\phi)^\xi e^{r \xi}
      }
      \int_0^\infty
      {1 \over (x + K)^{\alpha + 1}}
      \left(1 + {x \over K}\right)
      dx \\
      &=&
      {
        p \alpha (1 + b)
        \over
        \xi (\alpha - 1) (1 - \hat\phi)^\xi e^{r \xi}
      } < \infty
    \end{eqnarray*}
    Let
    \begin{eqnarray}
      c &:=& {p \over \xi}
        (1 + b)\int_{0}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      {
        \alpha K^{\alpha} dx \over (K + x)^{\alpha + 2}
      } \nonumber \\
      &<&
      {
        \alpha K^\alpha p (1 + b)
        \over
        \xi (1 - \hat\phi)^\xi e^{r \xi}
      }
      \int_{0}^{\infty}
      {
        dx \over (K + x)^{\alpha + 2}
      } \nonumber \\
      &=& {
        \alpha p (1 + b)
        \over
        K \xi (\alpha + 1) (1 - \phi)^\xi e^{r \xi}
      } < \infty
      \label{eq:c_lower_bound}
    \end{eqnarray}
    Define distribution function $H(x): [0, \infty] \to [0, 1]$ by its
    density with respect to the Lebesgue measure
    \[
    {d H(x) \over d x}
    =
    {p (1 + b)\over c \xi}
    \left[
      (1 - \hat\phi) e^r + \hat\phi e^{-x}
    \right]^{-\xi}
    {
      \alpha K^{\alpha}
      \over
      (K + x)^{\alpha + 2}
    }
    \]
    Let $Y \sim H$, then
    \begin{eqnarray*}
      \E Y &:=& {p (1 + b)\over c \xi}
      \int_0^\infty
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi} {
        \alpha K^{\alpha} x dx
        \over
        (K + x)^{\alpha + 2}
      } \\
      &=& {\alpha L_2 \over c} - K \\
      L_1 &=& c \E \left[
        (Y + K) \ln \left(1 + {Y \over K} \right)
      \right]
    \end{eqnarray*}
    Notice
    \[
    {
      d^2
      \over
      dx^2
    }
    \left[
      (x + K) \ln\left(1 + {x \over K}\right)
    \right] = {1 \over x + K} > 0
    \quad \text{ for } x > 0
    \]
    That is, $(x + K) \ln(1 + x/K)$ defined on $[0, \infty]$ is a convex
    function. Now that $L_1, L_2 < \infty$, Jensen's inequality gives
    \[
    {L_1 \over c} = \E \left[
      (Y + K) \ln \left(1 + {Y \over K} \right)
    \right]
    >
    (\E Y + K) \times \ln(1 + \E Y/K)
    =
    {\alpha L_2  \over c}
    \ln\left(
      {\alpha L_2  \over c}
    \right)
    \]
    Therefore
    \[
    L_1 - L_2 > L_2 \left[
      \alpha \ln \left(
        {\alpha L_2 \over c}
      \right) - 1
    \right]
    \]
    Clearly $L_2 > 0$. So it remains to show
    \[
    \alpha \ln \left(
      {\alpha L_2 \over c}
    \right) - 1 > 0
    \]
    Or equivalently
    \begin{equation}
      \label{eq:xxie5}
      {L_2 \over c} > {1 \over \alpha} \exp\left( {1 \over \alpha} \right)
    \end{equation}
    Observe
    \begin{eqnarray*}
      L_2 &>&
      {p (1 + b) \over \xi}
      \int_{0}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi
      \right]^{-\xi}
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=& {
        p (1 + b)
        \over
        \alpha \xi ((1 - \phi) e^r + \phi)^\xi
      } 
    \end{eqnarray*}
    Meanwhile, as computed earlier in \eqref{eq:c_lower_bound}
    \[
      c < {
        \alpha p (1 + b)
        \over
        K \xi (\alpha + 1) (1 - \phi)^\xi e^{r \xi}
      }
    \]
    Thus, to show inequality \eqref{eq:xxie5}, it is sufficient to show
    \begin{equation}
      \label{eq:xxie6}
      {
        \left[
          b (K + q)^{-\alpha} + K^{-\alpha}
        \right]
        \left[
          (1 - \hat\phi) e^r
        \right]^{\xi}
        (\alpha + 1)
        \over
        \alpha^2
        \left[
          b (K + q)^{-\alpha - 1} + K^{-\alpha - 1}
        \right]
        \left[
          (1 - \hat\phi) e^r + \hat\phi
        \right]^{\xi}
      } > {1 \over \alpha} \exp\left( {1 \over \alpha} \right)
    \end{equation}
    This expression can be simplified to
    \begin{eqnarray}
      \left(
           {\hat\phi \over 1 - \hat\phi} e^{-r} + 1
      \right)^{-\xi} &>&
      {
        \alpha e^{1/\alpha} \left[
          (K + q)^{-\alpha - 1} b + K^{-\alpha - 1}
        \right]
        \over
        (\alpha + 1) \left[
          (K + q)^{-\alpha} b + K^{-\alpha}
        \right]
      } \nonumber \\
      {\hat\phi \over 1 - \hat\phi}e^{-r} + 1
      &<&
      \left[
        {\alpha + 1 \over \alpha}
        {
          b K^{\alpha + 1} (K + q)
          + (K + q)^{\alpha + 1} K 
          \over
          b K^{\alpha + 1} + (K + q)^{\alpha + 1}
        } {
          1
          \over
          e^{1/\alpha}
        }
     \right]^{1/\xi} \nonumber \\
      &=&
      \left[
        {\alpha + 1 \over \alpha}
        {
          b \left(1 + {q \over K}\right)
          + \left(1 + {q \over K}\right)^{\alpha + 1}
          \over
          b + \left(1 + {q \over K}\right)^{\alpha + 1}
        } {
          K
          \over
          e^{1/\alpha}
        }
      \right]^{1/\xi} \nonumber \\
      \hat\phi &<& {1 - g \over 1 - g - e^{-r}}
      \label{eq:xxie7}
    \end{eqnarray}
    where
    \[
    g = 
    \left[
      {\alpha + 1 \over \alpha}
      {
        b \left(1 + {q \over K}\right)
        + \left(1 + {q \over K}\right)^{\alpha + 1}
        \over
        b + \left(1 + {q \over K}\right)^{\alpha + 1}
      } {
        K
        \over
        e^{1/\alpha}
      }
      \right]^{1/\xi}
    \]
    Inequality \eqref{eq:xxie7} is satisfied by all possible
    $\hat\phi$ if
    \begin{eqnarray*}
      g &<& 1 - e^{-r}
    \end{eqnarray*}
    Observe that the expression
    \[
    {
      b \left(1 + {q \over K}\right)
      + \left(1 + {q \over K}\right)^{\alpha + 1}
      \over
      b + \left(1 + {q \over K}\right)^{\alpha + 1}
    }
    \]
    is 1 and increasing at $q = 0$; as $q \to \infty$, it tends to
    1. So it must have a maximum value for
    $q \in (0, \infty)$. Let
    \[
    A = \max_{x \geq 1} {b x + x^{\alpha + 1} \over b + x^{\alpha + 1}}
    \]
    Then $g < 1 - e^{-r}$ is implied by
    \begin{eqnarray*}
      {\alpha + 1 \over \alpha}
      {K \over e^{1/\alpha}}
      A &<& (1 - e^{-r})^\xi \\
      K &<& {
        \alpha e^{1/\alpha} (1 - e^{-r})^\xi
        \over
        (\alpha + 1) A
      }
    \end{eqnarray*}
    The last inequality is indeed assumption \eqref{eq:xxie1.1}.
    So, under this assumption, \eqref{eq:xxie7} is satisfied by all
    $\hat\phi$ and \eqref{eq:xxie6} holds. We conclude
    \[
    \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) > 0
    \]
\end{proof}
Since $u(v) + b u(\delta v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$, all agents guided by this class of utility
functions will seek the largest $\alpha$ found in a stock group e.g.
a sector. As a result, one can expect all the actively traded equities
in the group to feature the same $\alpha$. In section
\ref{sec:data_analysis} we analyse real-world data of stock returns to
verify this conclusion.

In comparison to the theoretical constancy of $\alpha$, the scale and
shift parameter $K$ in the lower-tail distribution of $X$ may vary
hugely from one equity to another. This could be understood by observing
\[
\lim_{K \to 0} F(x) = \left\{
\begin{array}{ll}
  p \delta_0((-\infty, x])) & \text{ if } x \leq 0 \\
  1 - (1 - p) \left(
    K' \over K' + x
  \right)^\beta & \text{ if } x > 0
\end{array}
\right.
\]

\section{Review of multivariate GARCH models:
  same tail index or not}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).

>>>>

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\begin{eqnarray}
u(v) &=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) \P[C < \delta v] \nonumber \\
&=& \E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q) \label{eq:functional}
\end{eqnarray}
where
\begin{eqnarray*}
  q(r, \phi) &:=& \ln \left( {
    \delta v - (1 - \phi) e^r
    \over
    \phi
} \right) = \ln\left(
e^r + {\delta v - e^r \over \phi}
\right)
\end{eqnarray*}
Note $C < \delta v$ implies
\[
X < q(r, \phi)
\]
Naturally, if an agent invests in a risky asset instead of a riskless
bond, he expects to obtain a higher return from the risky asset than
he is guarranteed from the riskless bond. In our notation,
this means $\delta v > e^r$, which implies $q(r, \phi) > 0$.
The right-hand-side of \eqref{eq:functional} is a functional of the
distribution function of $X$ via \eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v] - b u(\delta v) F(q(r, \phi))
\]
Hereafter we abbreviate $q(r, \phi)$ to just $q$. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \over (K - x)^{\alpha + 1}} dx
  \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < q} \over (K' + x)^{\beta + 1}} dx \nonumber \\
  &&
  - b u(\delta v) \left[
    1 - (1 - p) {
      K'^\beta
      \over
      (K' + q)^\beta
    }
  \right]
  \label{eq:xxie1.0}
\end{eqnarray}
Let
\[
G(\alpha, \beta, K, K') =
\max_{0 < \phi \leq 1} \mathcal U F(\alpha, \beta, K, K', \phi)
\]

\begin{theorem} \label{thrm:I}
  Let the disappointment threshold $C < \delta v$ be equivalent to $X
  < q$. Assume $q > 0$. Then $G(\alpha, \beta, K, K')$ is
  monotonically increasing with $\alpha$.
\end{theorem}

\begin{proof}
  We show
  \[
  \td{G}{\alpha} > 0
  \]
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \argmax_{0 < \phi \leq 1}
    \mathcal U F(\alpha, \beta, K, K', \phi)
  \end{equation}
  We have
  \[
  G(\alpha, \beta, K, K') = \mathcal U F(\alpha, \beta, K, K', \hat \phi)
  \]
  It follows
  \begin{eqnarray}
    \td{G}{\alpha}
    &=&
    \pd{\mathcal U F}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    + \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi)
    \pd{\hat \phi}{\alpha}(\alpha, \beta, K, K')
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    \pd{\mathcal U F}{\phi}(\alpha, \beta, K, K', \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi)
    &>& 0
  \end{eqnarray*}
  We have
    \begin{eqnarray*}
      && \pd{\mathcal U(F)}{\alpha}(\alpha, \beta, K, K', \hat \phi) \\
      &=&
      - \frac{\partial}{\partial \alpha} \left\{
        {\alpha p K^\alpha \over \xi} (1 + b)
        \int_{-\infty}^{0}
          \left[
            (1 - \hat\phi) e^r + \hat\phi e^x
          \right]^{-\xi}
          (K - x)^{-\alpha - 1}
        dx \right\} \\
      &=&
      {p \over \xi}
      (1 + b)
      \int_{0}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=&
      - {p \over \xi}
      (1 + b)
      \int_{0}^{h}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        1 - \alpha \ln \left(
          1 + {x \over K}
        \right)
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &&
      + {p \over \xi}
      (1 + b)
      \int_{h}^{\infty}
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-x}
      \right]^{-\xi}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &>&
      - {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{0}^{h}
      \left[
        1 - \alpha \ln \left(
          1 + {x \over K}
        \right)
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &&
      + {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{h}^{\infty}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=&
      {p \over \xi}
      (1 + b)
      \left[
        (1 - \hat\phi) e^r + \hat\phi e^{-h}
      \right]^{-\xi}
      \int_{0}^{\infty}
      \left[
        \alpha \ln \left(
          1 + {x \over K}
        \right) - 1
      \right]
      {K^{\alpha} dx
        \over
        (K + x)^{\alpha + 1}
      } \\
      &=& 0
    \end{eqnarray*}
    where
    \[
    h = (e^{1/\alpha} - 1)K
    \]
  \end{proof}
Since $u(v)$ given in \eqref{eq:xxie1.0} as a
functional of the distribution function of $X$ is increasing with the
lower tail index $\alpha$, all agents guided by this class of utility
functions will seek the largest $\alpha$ found in a stock group e.g.
a sector. As a result, one can expect all the actively traded equities
in the group to feature the same $\alpha$. In section
\ref{sec:data_analysis} we analyse real-world data of stock returns to
verify this conclusion.

In comparison to the theoretical constancy of $\alpha$, the scale and
shift parameter $K$ in the lower-tail distribution of $X$ may vary
hugely from one equity to another. This could be explained by
\[
\lim_{K \to 0} \td{G}{K}(\alpha, \beta, K, K', \phi) = 0
\]
When $K$ is very small, as is the case in real-world stock return
distributions, a change of $K$ makes little difference to the utility
functional, so its value can vary drastically.

\begin{theorem}
  Assume $K \leq 1$.
  \[
  \lim_{K \to 0} \td{G}{K}(\alpha, \beta, K, K') = 0
  \]
\end{theorem}
\begin{proof}
  By the same argument as in the proof of theorem \ref{thrm:I}, it
  suffices to show
  \begin{eqnarray*}
    \lim_{K \to 0}
    \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat \phi) &=& 0
  \end{eqnarray*}
  The left-hand-side is
  \begin{eqnarray*}
    && \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat \phi) \\
    &=&
    -{\alpha p (1 + b) \over \xi}
    \int_{-\infty}^0
    {
      1 \over
      \left[
        (1 - \phi) e^r + \phi e^x
      \right]^\xi
    }
    {
      K^{\alpha - 1}
      (\alpha x + K)
      \over
      (K - x)^{\alpha + 2}
    } dx  \\
    &=&
    {\alpha p (1 + b) \over \xi}
    \int_0^{\infty}
    {
      1 \over
      \left[
        (1 - \phi) e^r + \phi e^x
      \right]^\xi
    }
    {
      K^{\alpha - 1}
      (\alpha x - K)
      \over
      (K + x)^{\alpha + 2}
    } dx
  \end{eqnarray*}
  By reverse Fatou's lemma, it follows
  \begin{eqnarray*}
    &&
    \lim_{K \to 0} \sup_{0 \leq M \leq K}
    \pd{\mathcal U(F)}{K}(\alpha, \beta, K, K', \hat \phi) \\
    &\leq&
    {\alpha p (1 + b) \over \xi}
    \int_0^{\infty}
    {
      1 \over
      \left[
        (1 - \phi) e^r + \phi e^x
      \right]^\xi
    }
    \lim_{K \to 0} \sup_{0 \leq M \leq K}
    {
      M^{\alpha - 1}
      (\alpha x - M)
      \over
      (M + x)^{\alpha + 2}
    } dx
  \end{eqnarray*}
\end{proof}
\section{Review of multivariate GARCH models:
  same tail index or not}
Many multivariate GARCH models imply a common tail index for all
series under consideration, e.g. the Orthogonal GARCH model of
Alexander and Chibumba (1997) \cite{alexander1997multivariate}, its
generalization GO-GARCH of van der Weide (2002) \cite{van2002go}, as
well as the Full Factor GARCH model of Vrontos et al (2003)
\cite{vrontos2003full} and the Generalized Orthogonal Factor GARCH
model of Lanne and Saikkonen (2007) \cite{lanne2007modeling}. These
models are characterized by their treatment of each series as a linear
combination of factors, and each of the factors is modeled as a GARCH
process. As a result of this treatment, each and every series under
consideration necessarily has the lowest of the tail indices of its
contributing factors (cf. Mikosch (2013) \cite{Mikosch2013} as well
as Andersen, Davis, Kreiss and Mikosch (2009)
\cite{andersen2009handbook}).
